Luminance constancy under fixed geometry

### 2018-02-07 Draft2/draft2.tex
more edits

AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction. When provided with a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task. The task is implicitly defined in terms of the labels. The optimal filters that are returned by AMA are the filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set. Once these filters have been identified, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.

{\bf Learning AMA Filters:} Let us assume that there are $N_{\nu}$ possible values of the labels. In our analysis, it means that the luminance level of the target object in an image can take one of the possible $N_{\nu}$ values ($\{Y_k: k\in[1,N_{\nu}] \}$). We represent the $l$'th image corresponding to the $k$'th label as $s_{kl}$. Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$. Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the label ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$. Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and an avearge cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.

@@

{\bf Estimating labels:} The image labels are estimated using the Bayesian decoder as described above. First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$. We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$. To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$. The estimated value is the one that optimizes the cost function.

>>>>

To construct an ideal observer model for our task, two steps are required. First, we use AMA to learn the filters that are optimal for the task. Second, we determine how to optimally decode the task relevant variable from the filter responses to arbitrary stimuli.

{\bf Learning optimal filters:} AMA \cite{geisler2009optimal,burge2017accuracy} is a task specific Bayesian method for dimensionality reduction. When provided with a labeled training set, a response noise model, and a cost function, AMA returns the linear receptive fields in rank order that are optimal for performing a task. The optimal filters that are returned by AMA are the filters whose noisy responses to the stimuli, as given by the specified response model, minimizes the cost function over the training set when optimally decoded.

Let us assume that there are $N_{\nu}$ possible values of the target object luminance levels ($\{Y_k: k\in[1,N_{\nu}] \}$). We represent the $l$'th image corresponding to the $k$'th level as $s_{kl}$. Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$. Let's say we have a decoder $g$, that uses the information of the response noise model, to return the Bayes optimal estimate of the luminance level ($\hat{Y}_k$) corresponding to the stimuli $s_{kl}$. Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and an avearge cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.

@@

{\bf Estimating labels:}

Once these filters have been learned, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.

The image labels are estimated using the Bayesian decoder as described above. First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$. We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$. To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$. The estimated value is the one that optimizes the cost function.
